PRIMUS: Quiescent Fraction as a Function of Environment and Redshift

### 2014-04-17 qfenv_paper/qf_environment.tex
Significant additions to SMF and QF sections

\section{Stellar Mass Function} \label{sec:smf}
The target galaxy sample defined above has so far
been classified into quiescent or star-forming and 
dense or sparse. We further divide these subsamples 
into bins of redshift:  in redshift bins of $0.0375-0.145$, 
$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
PRIMUS data ranges from $0.2 < z < 1.2$, we only 
consider galaxies with $ z<0.8$ due to insufficient
statistics for robust environment measurements at 
higher redshifts. With added redshift bins, we have a
total of 16 subsamples. We calculate the SMF for 
each of these 16 subsamples.

@@

\section{Quiescent Fraction} \label{sec:qf_const}
From the SMF number densities ($\Phi$) calculated
in the previous section, the quiescent fraction is computed 
as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies 
per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ 
for the quiescent and star-forming subsamples, respectively 
(Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for dense 
and spare environments over our redshift range as plotted in
 Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ 
 for dense (right) and sparse (left) environments. As in 
 Figure \ref{fig:smf}, the darker shading represent lower redshifts.

For both the spare and dense environments there is a notable 
increase in $f_{\rm{Q}}$ at all stellar masses as redshift decreases.
%%% INCLUDE BRIEF QUALITATIVE ANALYSIS OF THE EVOLUTION OF THE QUIESCENT FRACTION

In order to compare the $\rm{QF}$s at different redshift for each of the environment classifications, we perform a linear least squares fit on the $\rm{QF}$ for all the $\rm{QF}$s. 
Then we use the value of the linear fit at an empirically selected fiducial mass $\rm{log} \: \mathcal{M}/\mathcal{M}_{\odot} = 10.5$ (using fiducial mass of $\rm{log} \: \mathcal{M}/
\mathcal{M}_\odot = 11.0$ does not noteably change the outcome).
These values are used to highlight and attempt to quantify the differences of the $\rm{QFs}$ at the different redshifts, Figure \ref{fig:qf}
%of the low redshift and low environemnt subsample.
%The slope obtained from this fit is then used to perform a lienar fit for the rest of the $\rm{QF}$s.

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.png}
        \label{fig:qffit}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for 
low (square) and high (circle) environments in the redshift range $z = 0 - 0.8$. The evolution of 
$f_{Q}(\mathcal{M}_{\rm{fid}})$ for galaxies in different environments shows an evolution over the redshift
range that is independent of environment density. Futhermore throughout the redshift range the difference in 
$f_{Q}(\mathcal{M}_{\rm{fid}})$ remains relatively constant and $ < 0.15$.}
    \end{center}
\end{figure}

>>>>

\section{Stellar Mass Function} \label{sec:smf}
The target galaxy sample defined above has so far
been classified into quiescent or star-forming and 
dense or sparse. We further divide these subsamples 
into bins of redshift: $0.0375-0.145$, 
$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
PRIMUS data ranges from $0.2 < z < 1.2$, we only 
consider galaxies with $ z<0.8$ due to insufficient
statistics for robust environment measurements at 
$z > 0.8$. With added redshift bins, we have a
total of 16 subsamples. We calculate the SMF for 
each of these 16 subsamples. 
%% EMPHASIZE THE FACT THAT WE HAVE ENVIRONMENT MEASURES AND A ROBUST ENOUGH DATA TO PROBE 
%% UP TO REDSHIFT 0.7! THAT WAY WE CAN SEE THE MASS DISTRIBUTION OF VERY SPECIFIC POPULATIONS OF
%% GALAXIES UP TO A PRETTY HIGH REDSHIFT!

@@

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section describe
the distribution of our galaxy population in stellar mass 
and reveal the evolution of this distribution
over comic time. From the SMFs, we 
compute the quiescent fractions in order to compare the 
quiescent and the star-forming populations 
and to quantify the fraction of galaxies that have
depleted their star-formation. Furthermore, by dividing our 
galaxy sample using environment measurements into dense
and sparse samples, we investigate the environment 
dependence on the quiescent fraction and consequently 
on environment dependent quenching mechanisms.

From the SMF number densities ($\Phi$)
in the previous section, the quiescent fraction is computed 
as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies 
per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ 
for the quiescent and star-forming subsamples, respectively 
(Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for dense 
and spare environments over our redshift range as plotted in
 Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ 
 for dense (right) and sparse (left) environments. As in 
 Figure \ref{fig:smf}, the darker shading represent lower redshifts.

In both sparse and dense environments, Figure \ref{fig:qf}
clearly shows an increase in $f_{\rm{Q}}$ with decrease in redshift at all 
stellar masses. Qualitatively, this $f_{\rm{Q}}$ evolution 
exhibits a notable mass dependence. More specifically, 
the $f_{\rm{Q}}$ in sparse environments shows a greater 
evolution between redshift bins at high masses than at low 
masses. On the other hand, the $f_{\rm{Q}}$ in dense 
environments shows a greater evolution between redshift 
bins at low masses than at high masses.

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_25_fidmass10_5_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for sparse (square) and dense (circle) environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, $f_{Q}(\mathcal{M}_{\rm{fid}})$ for dense environment is greater than $f_{Q}(\mathcal{M}_{\rm{fid}})$ for lower environment. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}
%fiducial mass may be 11.0 depending on what we want.
% fixed slope? Can't do fixed slope if we say there is mass dependence in f_q evolution

While trends are apparent from Figure \ref{fig:qf}, quantitative comparisons of the 
$f_{\rm{Q}}$ for different environment over redshift is made challenging by the distinct stellar mass 
completeness limits for each redshift bin. In order to quantify the quiescent fraction over the stellar mass complete rate, we fit each $f_{\rm{Q}}$ to a power-law parameterization as a function of stellar mass, 
\begin{equation} 
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}).
The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected
fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass completeness limits. This fiducial mass 
serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts and using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$ 
does not notably alter the results. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ 
for sparse (diamond) and dense (circle) environments.
For both dense and spare environments, $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases. In addition, through the redshift range explored in our analysis, dense environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ is significantly greater than the sparse environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$. However when we compute $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{dense}} - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{sparse}}$, we find the difference remains constant throughout the redshift range ($ < 0.15$ throughout redshift range). Furthermore, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show no strong environment dependence.

The analysis described in this paper use a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment, the same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper.
